---
title: "Carolina Climb Everest Challenge"
date: "Last Updated: `r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: cerulean
    highlight: tango
    toc: false
    toc_depth: 2
    toc_float: true
    css: styles.css  # Reference to the custom CSS file
  pdf_document: 
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
library(knitr)
library(kableExtra)
```

Welcome to the Carolina Climb Everest Challenge. Can you take down over 11000 feet of climbing in one semester? If you're ready to get started, go submit your first climb!

## How to Sign Up

Ready to join the challenge? [Click here to log a climb!](https://forms.office.com/Pages/ResponsePage.aspx?id=T9WzWMkW00KvCB_KvQlWZpdqpBijr_pOhAYAv-Ww5RFUODdVVjlaU1pFWU9YVkpNUUxTRUxaNTM4OC4u) Simply log your climbs, and see how you stack up against other competitors. The more you climb, the higher you'll rank!

---

\


```{r, include=FALSE}
# Load necessary libraries
library(dplyr)
library(knitr)
library(readr)

df1 <- read_csv("Carolina Climbing Challenge 2024(Sheet1).csv")

# Sample data, replace this with your actual dataset
df <- data.frame(
  Id = 1,
  Start_time = "9/3/24 15:45",
  Completion_time = "9/3/24 15:46",
  Email = "anonymous",
  Name = "",
  First_and_Last_Name = "Jake Flaherty",
  PID = 730545177,
  Top_Rope_Routes = 5,
  Boulders = 5,
  Wall = "Fetzer",
  Climb_Date = "9/3/24"
)

# Calculate total feet climbed
df <- df1 %>%
  mutate(
    `Total_Feet_Climbed` = sum((Top_Rope_Routes * 30) + (Boulders * 12), na.rm = TRUE))

compMTC <- df %>%
  group_by(PID) %>%
  summarise(
    `Full Name` = first(First_and_Last_Name),  # Assuming names are consistent across rows for each PID
    `Top Rope Routes Climbed` = sum(Top_Rope_Routes, na.rm = TRUE),
    `Boulders Climbed` = sum(Boulders, na.rm = TRUE),
    `Total Distance (ft)` = sum((Top_Rope_Routes * 30) + (Boulders * 12), na.rm = TRUE)
  ) %>%
  select(`Full Name`, `Top Rope Routes Climbed`, `Boulders Climbed`, `Total Distance (ft)`) %>%
  arrange(desc(`Total Distance (ft)`))

# Filter those above 10,000 feet
above_10k <- compMTC %>%
  filter(`Total Distance (ft)` > 5495) 


```

## 2025 Everest Climbers

```{r, echo=FALSE}
# Display the table
kable(above_10k) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = TRUE)
```

---

\

```{r, include=FALSE}

competitors <- df %>%
  group_by(PID) %>%
  summarise(
    `Full Name` = first(First_and_Last_Name),  # Assuming names are consistent across rows for each PID
    `Top Rope Routes Climbed` = sum(Top_Rope_Routes, na.rm = TRUE),
    `Boulders Climbed` = sum(Boulders, na.rm = TRUE),
    `Total Distance (ft)` = sum((Top_Rope_Routes * 30) + (Boulders * 12), na.rm = TRUE)
  ) %>%
  select(`Full Name`, `Top Rope Routes Climbed`, `Boulders Climbed`, `Total Distance (ft)`) %>%
  arrange(desc(`Total Distance (ft)`))

#Competitors
competitors2 <- df %>%
  distinct(PID, .keep_all = TRUE) %>%
  mutate(Total_Feet_Climbed = (Top_Rope_Routes * 30) + (Boulders * 12)) %>%
  select(First_and_Last_Name, Top_Rope_Routes, Boulders, Total_Feet_Climbed) %>%
  rename(
    `Full Name` = First_and_Last_Name,
    `Top Rope Routes Climbed` = Top_Rope_Routes,
    `Boulders Climbed` = Boulders,
    `Total Distance (ft)` = `Total_Feet_Climbed`
  ) %>%
  arrange(desc(`Total Distance (ft)`))
```

## Competitors

```{r, echo=FALSE}
kable(competitors) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = TRUE) #%>%
#  row_spec(1:1, background = "#FFD700") %>%  
#  row_spec(2:2, background = "#C0C0C0") %>%
#  row_spec(3:3, background = "#CD7F32") %>%
#  row_spec(4:15, background = "#ebebeb")

##Add back later
```

